Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-05-04 paper/results.tex
Adding results
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@606 3fc257bb-8550-0410-81b3-a5c103da83f7

We ran each of the algorithms on three R-MAT graphs of
different sizes, each on a varying number of processors.  Details of the
input data are shown in Table~\ref{t:rmats}.
The {\it small} problem size (around 134M edges) was a 
problem that could be run
on a single processor.  The {\it medium} problem size (around 2B
edges) could be run on a few processors.  The {\it large} problem size
(around 34B edges) required most of the machine to run.
All data sets used R-MAT parameters $(a, b, c, d) = (0.57, 0.19, 0.19, 0.05)$.

\begin{table}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Data & \# of    & \# of & Maximum \\
Set  & vertices & edges & vertex degree\\
\hline
small  &$2^{24} \approx 17M$ & $2^{27} \approx 134M$ &   \\
medium &$2^{28} \approx 268M$ & $2^{31} \approx 2B$&   \\
large  &$2^{32} \approx 4B$ & $2^{35} \approx 34B$ &   \\
\hline
\end{tabular}
\caption{Characteristics of R-MAT input data for graph algorithm
experiments.}
\label{t:rmats}
\end{table}

The resulting timings give a sense of the inherent scalability of the
MapReduce algorithms as graph size grows on a fixed number of
processors, and of the parallel scalability for computing on a graph
of fixed size on a growing number of processors.

>>>>

We ran each of the algorithms on four R-MAT graphs of
different sizes, each on a varying number of processors.  Details of the
input data are shown in Table~\ref{t:rmats}.
The {\it tiny} problem size (around 8M edges) can typically be used
on a single processor without significant out-of-core operations.
The {\it small} problem size (around 134M edges) is a 
problem that can be run
on a single processor with out-of-core operations; larger processor 
configurations, however, do not necessary need out-of-core operations.
The {\it medium} problem size (around 2B
edges) can be used on a few processors.  The {\it large} problem size
(around 34B edges) requires most of the machine to run.
All data sets used R-MAT parameters $(a, b, c, d) = (0.57, 0.19, 0.19, 0.05)$.

\begin{table}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Data & \# of    & \# of & Maximum \\
Set  & vertices & edges & vertex degree\\
\hline
tiny   &$2^{20} \approx 1M$ & $2^{23} \approx 8M$ &   \\
small  &$2^{24} \approx 17M$ & $2^{27} \approx 134M$ &   \\
medium &$2^{28} \approx 268M$ & $2^{31} \approx 2B$&   \\
large  &$2^{32} \approx 4B$ & $2^{35} \approx 34B$ &   \\
\hline
\end{tabular}
\caption{Characteristics of R-MAT input data for graph algorithm
experiments.}
\label{t:rmats}
\end{table}

The resulting timings give a sense of the inherent scalability of the
MapReduce algorithms as graph size grows on a fixed number of
processors, and of the parallel scalability for computing on a graph
of fixed size on a growing number of processors.  Where available, we
compare the MapReduce algorithm with other parallel implementations.
